Machine Learning Tools for Open Cluster Characterization with Gaia DR2 Data

### 2021-01-17 thesis/thesis.tex
thesis: Review Results

Finally, we can refine this selection by filtering those stars which are bellow and above
the 0.25 and 0.75 quantiles for each group, respectively.
That way we remove the most doubtful values from the selection.
Figure \ref{fig:melotte_22_filtered} shows the result after filtering DEC clustering selection.

@@

Table \ref{tab:results_melotte_22} shows a summary of Melotte 22 with values taken from different sources and methods:
SIMBAD Astronomical Database - CDS (Strasbourg),
Clusterix+TOPCAT method, and the results obtained for each step of this method (KMeans, DEC and DEC filtered).
The errors associated to KMeans and DEC predictions are calculated as the Standard Error $SE = \sigma / \sqrt{N}$,
where $N$ is the number of samples in the selected group.

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr}\tablefootnote{Results have been taken from \protect\citeA[p.~25. Table A.3. Pleiades]{babusiaux2018gaia}} &
        19.997 $\pm$ 0.127 & -45.548 $\pm$ 0.101 & 7.364 $\pm$ 0.005 & 1326 \\
      Clusterix+TOPCAT & 19.98 $\pm$ 1.25 & -45.47 $\pm$ 1.48 & 7.33 $\pm$ 0.21 & 634 \\
      KMeans & 20.25 $\pm$ 0.95 & -38.01 $\pm$ 1.08 & 7.23 $\pm$ 0.06 & 1378 \\
      DEC & 23.67 $\pm$ 1.29 & -46.23 $\pm$ 1.50 & 8.04 $\pm$ 0.09 & 878 \\
      \textbf{DEC (filtered)} & 19.50 $\pm$ 0.41 & -44.23 $\pm$ 0.39 & 7.42 $\pm$ 0.005 & 438 \\
    \end{tabular}
    \caption{Parameters shown are proper motion in right ascension and declination, parallax
             with their respective deviations and number of stars corresponding to Melotte 22 data.}
    \label{tab:results_melotte_22}
  \end{center}
\end{table}

@@

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/pm_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/parallax_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/hr_diagram_ngc_2516.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2516 Clusterix+TOPCAT characterization.}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/kmeans_pm_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/kmeans_parallax_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/kmeans_hr_diagram_ngc_2516.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2516 KMeans characterization.}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_pm_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_parallax_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_hr_diagram_ngc_2516.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2516 DEC characterization.}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_pm_filtered_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_parallax_filtered_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_hr_diagram_filtered_ngc_2516.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2516 DEC (filtered) characterization.}
\end{figure}

@@

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      Number of Clusters & 8 \\
      Clustering Layer & $\left[ 50, 50, 60 \right]$ \\
      Kernel Initializer Seed & 2 \\
      Quantil Threshold & 0.15 \\
    \end{tabular}
    \caption{NGC 2516 DEC model hyperparameters.}
    \label{tab:hyperparameters_ngc_2516}
  \end{center}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & -4.6579 $\pm$ 0.0075 & 11.1517 $\pm$ 0.0075 & 2.4118 $\pm$ 0.0006 & 1727 \\
      Clusterix+TOPCAT & -4.652 $\pm$ 0.523 & 11.203 $\pm$ 0.454 & 2.409 $\pm$ 0.127 & 638 \\
      KMeans & -4.344 $\pm$ 0.14 & 9.507 $\pm$ 0.19 & 2.268 $\pm$ 0.01 & 1542 \\
      DEC & -4.426 $\pm$ 0.17 & 9.952 $\pm$ 0.20 & 2.436 $\pm$ 0.01 & 1532 \\
      \textbf{DEC (filtered)} & -4.502 $\pm$ 0.14 & 10.114 $\pm$ 0.17 & 2.392 $\pm$ 0.004 & 1072 \\
    \end{tabular}
    \caption{NGC 2516 results.}
    \label{tab:results_ngc_2516}
  \end{center}
\end{table}

@@

\begin{figure}[H]
  \vfil
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/pm_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/parallax_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/hr_diagram_ngc_2632.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2632 Clusterix+TOPCAT characterization.}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/kmeans_pm_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/kmeans_parallax_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/kmeans_hr_diagram_ngc_2632.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2632 KMeans characterization.}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_pm_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_parallax_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_hr_diagram_ngc_2632.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2632 DEC characterization.}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_pm_filtered_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_parallax_filtered_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_hr_diagram_filtered_ngc_2632.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2632 DEC (filtered) characterization.}
\end{figure}

@@

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      Number of Clusters & 10 \\
      Clustering Layer & $\left[ 50, 50, 40 \right]$ \\
      Kernel Initializer Seed & 10 \\
      Quantil Threshold & 0.1 \\
    \end{tabular}
    \caption{NGC 2632 DEC model hyperparameters.}
    \label{tab:hyperparameters_ngc_2632}
  \end{center}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & -36.047 $\pm$ 0.110 & -12.917 $\pm$ 0.066 & 5.371 $\pm$ 0.003 & - \\
      Clusterix+TOPCAT & -36.154 $\pm$ 1.001 & -12.909 $\pm$ 0.806 & 5.327 $\pm$ 0.187 & 371 \\
      KMeans & -26.352 $\pm$ 0.82 & -15.828 $\pm$ 0.76 & 5.394 $\pm$ 0.03 & 629 \\
      DEC & -20.012 $\pm$ 0.69 & -14.742 $\pm$ 0.58 & 4.686 $\pm$ 0.03 & 894 \\
      \textbf{DEC (filtered)} & -21.571 $\pm$ 0.74 & -14.234 $\pm$ 0.61 & 4.719 $\pm$ 0.03 & 714 \\
    \end{tabular}
    \caption{NGC 2632 results.}
    \label{tab:results_ngc_2632}
  \end{center}
\end{table}

@@

\begin{figure}[H]
  \vfil
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/pm_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/parallax_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/hr_diagram_ngc_2682.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2682 Clusterix+TOPCAT characterization.}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/kmeans_pm_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/kmeans_parallax_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/kmeans_hr_diagram_ngc_2682.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2682 KMeans characterization.}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_pm_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_parallax_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_hr_diagram_ngc_2682.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2682 DEC characterization.}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_pm_filtered_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_parallax_filtered_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_hr_diagram_filtered_ngc_2682.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2682 DEC (filtered) characterization.}
\end{figure}

@@

@@

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      Number of Clusters & 10 \\
      Clustering Layer & $\left[ 50, 50, 40 \right]$ \\
      Kernel Initializer Seed & 0 \\
      Quantil Threshold & 0.1 \\
    \end{tabular}
    \caption{NGC 2682 DEC model hyperparameters.}
    \label{tab:hyperparameters_ngc_2682}
  \end{center}
\end{table}

>>>>

Finally, we can refine this selection by filtering those stars which are bellow and above
the 0.10 and 0.90 quantiles for each group, respectively.
That way we remove the most doubtful values from the selection.
Figure \ref{fig:melotte_22_filtered} shows the result after filtering DEC clustering selection.

@@

Table \ref{tab:results_melotte_22} shows a summary of Melotte 22 with values taken from different sources and methods:
SIMBAD Astronomical Database - CDS (Strasbourg),
Clusterix+TOPCAT method, and the results obtained for each step of this method (KMeans, DEC and DEC filtered).
Errors associated to KMeans and DEC predictions have been calculated as the \emph{Standard Error},
$SE = \sigma / \sqrt{N}$, where $N$ is the number of samples in the selected group.

\vfill
\begin{table}[h]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr}\tablefootnote{Results have been taken from \protect\citeA[p.~25. Table A.3. Pleiades]{babusiaux2018gaia}} &
        19.997 $\pm$ 0.127 & -45.548 $\pm$ 0.101 & 7.364 $\pm$ 0.005 & 1326 \\
      Clusterix+TOPCAT & 19.98 $\pm$ 1.25 & -45.47 $\pm$ 1.48 & 7.33 $\pm$ 0.21 & 634 \\
      KMeans & 20.25 $\pm$ 0.95 & -38.01 $\pm$ 1.08 & 7.23 $\pm$ 0.06 & 1378 \\
      DEC & 23.67 $\pm$ 1.29 & -46.23 $\pm$ 1.50 & 8.04 $\pm$ 0.09 & 878 \\
      \textbf{DEC (filtered)} & 19.50 $\pm$ 0.41 & -44.23 $\pm$ 0.39 & 7.42 $\pm$ 0.005 & 438 \\
    \end{tabular}
    \caption{Parameters shown are proper motion in right ascension and declination, parallax
             with their respective deviations and number of stars corresponding to Melotte 22 data.}
    \label{tab:results_melotte_22}
  \end{center}
\end{table}
\vfill

@@

\begin{figure}[H]
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/pm_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/parallax_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/hr_diagram_ngc_2516.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2516 Clusterix+TOPCAT characterization.}
  \label{fig:result_ngc_2516_clusterix}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/kmeans_pm_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/kmeans_parallax_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/kmeans_hr_diagram_ngc_2516.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2516 KMeans characterization. Identified as cluster \emph{g3}.}
  \label{fig:result_ngc_2516_kmeans}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_pm_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_parallax_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_hr_diagram_ngc_2516.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2516 DEC characterization. Identified as cluster \emph{g3}.}
  \label{fig:result_ngc_2516_dec}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_pm_filtered_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_parallax_filtered_ngc_2516.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2516/dec_hr_diagram_filtered_ngc_2516.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2516 DEC (filtered) characterization. Identified as cluster \emph{g3}.}
  \label{fig:result_ngc_2516_dec_filtered}
\end{figure}

@@

Figure \ref{fig:result_ngc_2516_clusterix} shows NGC 2516 characterized using Clusterix+TOPCAT tools.
Figure \ref{fig:result_ngc_2516_kmeans} shows eigth clusters identified by KMeans.
In this case, cluster \emph{g3} is the one we are looking for.
Figures \ref{fig:result_ngc_2516_dec} and \ref{fig:result_ngc_2516_dec_filtered}
show the groups found using the DEC model and the DEC model filtered, respectively.
Again, the cluster of interest is the group \emph{g3}.
Although in general, groups between KMeans model and DEC models may not match.

Table \ref{tab:hyperparameters_ngc_2516} shows the hyperparameters used for characterizing NGC 2516
with the DEC model. Table \ref{tab:results_ngc_2516} shows a results summary for NGC 2516.

@@

\begin{table}[h]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      Number of Clusters & 8 \\
      Clustering Layer & $\left[ 50, 50, 60 \right]$ \\
      Kernel Initializer Seed & 2 \\
      Quantil Threshold & 0.15 \\
    \end{tabular}
    \caption{NGC 2516 DEC model hyperparameters.}
    \label{tab:hyperparameters_ngc_2516}
  \end{center}
\end{table}

\begin{table}[h]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & -4.6579 $\pm$ 0.0075 & 11.1517 $\pm$ 0.0075 & 2.4118 $\pm$ 0.0006 & 1727 \\
      Clusterix+TOPCAT & -4.652 $\pm$ 0.523 & 11.203 $\pm$ 0.454 & 2.409 $\pm$ 0.127 & 638 \\
      KMeans & -4.344 $\pm$ 0.14 & 9.507 $\pm$ 0.19 & 2.268 $\pm$ 0.01 & 1542 \\
      DEC & -4.426 $\pm$ 0.17 & 9.952 $\pm$ 0.20 & 2.436 $\pm$ 0.01 & 1532 \\
      \textbf{DEC (filtered)} & -4.502 $\pm$ 0.14 & 10.114 $\pm$ 0.17 & 2.392 $\pm$ 0.004 & 1072 \\
    \end{tabular}
    \caption{NGC 2516 results.}
    \label{tab:results_ngc_2516}
  \end{center}
\end{table}

@@

\begin{figure}[H]
  \vfil
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/pm_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/parallax_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/hr_diagram_ngc_2632.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2632 Clusterix+TOPCAT characterization.}
  \label{fig:result_ngc_2632_clusterix}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/kmeans_pm_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/kmeans_parallax_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/kmeans_hr_diagram_ngc_2632.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2632 KMeans characterization. Identified as cluster \emph{g1}.}
  \label{fig:result_ngc_2632_kmeans}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_pm_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_parallax_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_hr_diagram_ngc_2632.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2632 DEC characterization. Identified as cluster \emph{g1}.}
  \label{fig:result_ngc_2632_dec}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_pm_filtered_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_parallax_filtered_ngc_2632.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2632/dec_hr_diagram_filtered_ngc_2632.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2632 DEC (filtered) characterization. Identified as cluster \emph{g1}.}
  \label{fig:result_ngc_2632_dec_filtered}
\end{figure}

@@

Figure \ref{fig:result_ngc_2632_clusterix} shows NGC 2632 characterized by the validation method.
Figure \ref{fig:result_ngc_2632_kmeans} shows ten clusters identified by KMeans.
Cluster \emph{g1} is the open cluster we are looking for.
Figures \ref{fig:result_ngc_2632_dec} and \ref{fig:result_ngc_2632_dec_filtered}
show the groups found using the DEC model and the DEC model filtered, respectively.
Open cluster NGC 2632 is labeled as group \emph{g1}.

Table \ref{tab:hyperparameters_ngc_2632} shows the hyperparameters used for characterizing NGC 2632
with our model. Table \ref{tab:results_ngc_2632} shows a results summary for NGC 2632 analysis.

@@

\begin{table}[h]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      Number of Clusters & 10 \\
      Clustering Layer & $\left[ 50, 50, 40 \right]$ \\
      Kernel Initializer Seed & 10 \\
      Quantil Threshold & 0.1 \\
    \end{tabular}
    \caption{NGC 2632 DEC model hyperparameters.}
    \label{tab:hyperparameters_ngc_2632}
  \end{center}
\end{table}

\begin{table}[h]
  \begin{center}
    \begin{tabular}{l|c|c|c|c}
      \textbf{Source / method} & \emph{$\mu_{\alpha}$ $(mas/yr^{-1})$} & \emph{$\mu_{\delta}$ $(mas/yr^{-1})$} & \emph{$\varpi$ $(mas)$} & \emph{\# stars} \\
      \hline
      \textbf{Simbad.u-strasbg.fr} & -36.047 $\pm$ 0.110 & -12.917 $\pm$ 0.066 & 5.371 $\pm$ 0.003 & - \\
      Clusterix+TOPCAT & -36.154 $\pm$ 1.001 & -12.909 $\pm$ 0.806 & 5.327 $\pm$ 0.187 & 371 \\
      KMeans & -26.352 $\pm$ 0.82 & -15.828 $\pm$ 0.76 & 5.394 $\pm$ 0.03 & 629 \\
      DEC & -20.012 $\pm$ 0.69 & -14.742 $\pm$ 0.58 & 4.686 $\pm$ 0.03 & 894 \\
      \textbf{DEC (filtered)} & -21.571 $\pm$ 0.74 & -14.234 $\pm$ 0.61 & 4.719 $\pm$ 0.03 & 714 \\
    \end{tabular}
    \caption{NGC 2632 results.}
    \label{tab:results_ngc_2632}
  \end{center}
\end{table}

@@

\begin{figure}[H]
  \vfil
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/pm_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/parallax_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/hr_diagram_ngc_2682.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2682 Clusterix+TOPCAT characterization.}
  \label{fig:result_ngc_2682_clusterix}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/kmeans_pm_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/kmeans_parallax_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/kmeans_hr_diagram_ngc_2682.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2682 KMeans characterization. Identified as cluster \emph{g4}.}
  \label{fig:result_ngc_2682_kmeans}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_pm_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_parallax_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_hr_diagram_ngc_2682.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2682 DEC characterization. Identified as cluster \emph{g2}.}
  \label{fig:result_ngc_2682_dec}
  \centering
  \begin{subfigure}{0.9\textwidth}
    \centering
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_pm_filtered_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_parallax_filtered_ngc_2682.png}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.30\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/ngc_2682/dec_hr_diagram_filtered_ngc_2682.png}
    \end{subfigure}
  \end{subfigure}
  \caption{NGC 2682 DEC (filtered) characterization. Identified as cluster \emph{g2}.}
  \label{fig:result_ngc_2682_dec_filtered}
\end{figure}

@@

Figure \ref{fig:result_ngc_2682_clusterix} shows NGC 2682 characterized using Clusterix+TOPCAT tools.
Figure \ref{fig:result_ngc_2682_kmeans} shows ten clusters identified by KMeans.
KMeans labels NGC 2682 as group \emph{g4}.
Figures \ref{fig:result_ngc_2682_dec} and \ref{fig:result_ngc_2682_dec_filtered}
show the groups found using the DEC model and the DEC model filtered, respectively.
The cluster of interest is the group \emph{g2}.

Table \ref{tab:hyperparameters_ngc_2682} shows the hyperparameters used for characterizing NGC 2682
with the DEC model. Table \ref{tab:results_ngc_2682} shows a results summary for NGC 2682.

@@

\begin{table}[h]
  \begin{center}
    \begin{tabular}{l|c}
      \textbf{Hyperparameter} & \textbf{Value} \\
      \hline
      Number of Clusters & 10 \\
      Clustering Layer & $\left[ 50, 50, 40 \right]$ \\
      Kernel Initializer Seed & 0 \\
      Quantil Threshold & 0.1 \\
    \end{tabular}
    \caption{NGC 2682 DEC model hyperparameters.}
    \label{tab:hyperparameters_ngc_2682}
  \end{center}
\end{table}
